Data Sources

### 2021-05-18 notebook/model-estimates.Rmd
in search of a better example

## GPDD

John Prendergast, Ellen Bazeley-White, Owen Smith, John Lawton, Pablo Inchausti, et al. 2010. The Global Population Dynamics Database. Knowledge Network for Biocomplexity. doi:10.5063/F1BZ63Z8.

```{r}
taxon <- read_csv(resolve("hash://md5/c996a91042243648fa0c803ac631803b", store=TRUE))
main <- read_csv(resolve("hash://md5/b7c5d86a5a2c44d6a303f09be1a8688a", store=TRUE))
data_source <- read_csv(resolve("hash://md5/22bf3d98318860b4cf5ea15179d5442b", store=TRUE))
ts <- read_csv(resolve("hash://md5/8eb14acec7eccfd342f11860909ce588", store=TRUE), guess_max = 1e6)
```

```{r}
# Redlist Data, from API via public token
pages <- ceiling(137210/10000) -1
query <- paste0("https://apiv3.iucnredlist.org/api/v3/species/page/", 0:pages,
"?token=9bb4facb6d23f48efbf424bb05c0c1ef1cf6f468393bc745d42179ac4aca5fee")
resp <- map(query, httr::GET)
redlist_status <- map_dfr(resp, function(r){
  x <- content(r)
  jsonlite::fromJSON(jsonlite::toJSON(x$result, auto_unbox = TRUE), flatten=TRUE)
})
is_global <- map_lgl(redlist_status$population, function(x) length(x) == 0)
redlist_endangered <- redlist_status %>% filter(category %in% c("CR", "EN"), is_global)
```

```{r}
# main timeseries data for only those species where complete Census is available
endagered <- taxon %>% 
  inner_join(redlist_endangered, by = c(TaxonName = "scientific_name")) %>%
  select(TaxonName,CommonName, TaxonID)
endagered  <- main %>% inner_join(endagered)
census <- endagered %>% filter(SamplingProtocol == "Count", grepl("Census", SamplingEffort))
census

```

```{r}
selected_ts <- ts %>% inner_join(census)

selected_ts %>%
  mutate(MainID = as.character(MainID)) %>%
  ggplot(aes(SeriesStep, Population, col=MainID)) +
  geom_point() + facet_wrap(~CommonName, scales="free")

## Focus on two populations of Macaca sylvanus, Barbary macaque, introduced in Gilbratar
selected_ts %>% filter(MainID %in% c(5019,5020)) %>% write_csv("barbary_macaque.csv")
```

```{r}
# Examine details about these studies from the original publications
data_source %>%
  inner_join(select(census, 
                    DataSourceID, 
                    MainID, 
                    TaxonName, 
                    CommonName), 
             by = c(DatasourceID = "DataSourceID"))
```

```{r}
#Access Biotime data, BioTIME Consortium. (2018). BioTIME (Version 2) [Data set]. Zenodo. http://doi.org/10.5281/zenodo.3265871
#biotime_csv <- resolve("hash://md5/e1b4b7fca5091584831d43a798086496", store=TRUE)
#biotime <- read_csv(biotime_csv, guess_max = 1e6)

```

>>>>

# May model fit

# Logistic model fit

# Allen model fit

# Transition matrices from ARIMA?
